\bf\mftitle

### 2011-02-18 doc/jInfer/basicxsd/basicxsd.tex
Documentation: BasicXSDExporter.

The main class implementing \code{SchemaGenerator} inference interface and simultaneously registered as its service provid\-er is \code{SchemaGeneratorImpl} in package \code{cz.cuni.mff.ksi.jinfer.basicxsd}. Process of export consists of two phases described in detail in later sections.
\begin{enumerate}
	\item Preprocessing.
	\item The export to a string representation itself.
\end{enumerate}
Method \code{start()} first creates an instance of \code{Preprocessor} class supplying the rules (elements) it got in the simplified grammar on input. Preprocessing itself is done by creating that instance (calling its constructor) and its results can be then retrieved by calling \code{getResult()} method. Purpose of preprocessing is to discover information necessary for export of elements. For example, determine elements which should be globally defined or which element is the root element.\\

@@

As mentioned above, preprocessing is implemented in \code{Preprocessor} class and its is the following following.
\begin{itemize}
	\item Decide which elements should be defined globally.
	\item Remove unused elements.
	\item Find the top level element.
	\item Find an instance of element by its name.
\end{itemize}

@@

Number of spaces characters per one level of indentation can be altered in project properties. See \ref{subsection:preferences}.

>>>>

The main class implementing \code{SchemaGenerator} inference interface and simultaneously registered as its service provi\-der is \code{SchemaGeneratorImpl} in package \code{cz.cuni.mff.ksi.jinfer.basicxsd}. Process of export consists of two phases described in detail in later sections.
\begin{enumerate}
	\item Preprocessing.
	\item The export to a string representation itself.
\end{enumerate}
Method \code{start()} first creates an instance of \code{Preprocessor} class supplying the rules (elements) it got in the simplified grammar on input. Preprocessing itself is done by creating that instance (calling its constructor) and its results can be then retrieved by calling \code{getResult()} method. Purpose of preprocessing is to discover information necessary for export of elements. For example, determine elements which should be globally defined or which element is the root element.\\

@@

As mentioned above, preprocessing is implemented in \code{Preprocessor} class and its purpose is the following.
\begin{itemize}
	\item Decide which elements should be defined globally.
	\item Remove unused elements.
	\item Find the top level element.
	\item Find an instance of element by its name.
\end{itemize}

@@

Number of spaces characters per one level of indentation can be altered in project properties, see \ref{subsection:preferences}.
